Covid-19 A Spatio-Temporal Investigation.

### 2021-01-09 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 The statistical software R (Version 4.0.3) was used to calculate the spatial and the spatio-temporal association, the Covid-19 database used in the study is also available in R, in a package called "COVID19" built by the *COVID-19 Data Hub* $\!\!^1\!^0$, the database begins in January 2020 and is constantly updated, it also gathers data from various sources of information for all countries in which it was possible to obtain data...

  que foi possível a obtenção de dados, também providencia as medidas políticas adotadas de acordo com o tempo durante a pandemia, no entanto há a presença de zeros no banco, mais precisamente na variável de casos recuperados, onde a China por exemplo permaneceu com o número zerado em todos os meses, o motivo não foi explicitado no site da *COVID-19 Data Hub*, no entanto supõe se a ausência ou inacessibilidade dessas informações para os países em que a incongruência ocorreu.

>>>>

 The statistical software R (Version 4.0.3) was used to calculate the spatial and the spatio-temporal association, the Covid-19 database used in the study is also available in R, in a package called "COVID19" built by the *COVID-19 Data Hub* $\!\!^1\!^0$, the database begins in January 2020 and is constantly updated, it also gathers data from various sources of information for all countries in which it was possible to obtain data. The database provides data about political measures adopted by each country during the pandemic, even though that information is not available for all countries included, which is one of the limitations of the database, that lack of data can also be seen in variables such as the number of recovered cases, where China for instance had no recovered cases during the analysis' period of time, since the reason for this was not explicit in the website of *COVID-19 Data Hub*, this paper supposes it was not possible to access data for countries which the information was lacking in the unified database.
